Old is Still Gold: A Comparison of Cyber and Traditional Consumer Fraud in The United States

### 2017-03-12 paper/paper.tex
tiny fixes

\title{Old is Still Gold: A Comparison of Cyber and Regular Consumer Fraud in The United States}

@@

While cybercrime is a relatively recent human invention, fraudulent activity
has a much longer history. Understanding the extent to which cybercrime is fundamentally different from, or similar to, traditional fraudulent activity is the first step toward being able to effectively combat it. This paper investigates the differences in fraud
reporting and targeting among United States based consumers by comparing
fraudulent activity mediated by the Internet with traditional forms of
fraud. By partitioning the FTC Consumer Sentinel complaint dataset into
cyber and traditional categories, we summarize the difference in fraud
trends across time, distance and location metrics.We also evaluate fraud
variations across different ethnic and socio-economic factors. Our findings
suggest that both categories of frauds experience an overall decrease during
the holiday season. Individuals who are victimized via traditional methods
are more likely to complain using traditional methods, while a majority of
cyber victims submit fraud complaints online. By evaluating the top frauds
in each category, we demonstrate how traditional fraudsters have evolved in
their methodologies to execute scams on the Internet that were initially
perpetrated through traditional means.

@@

We would like to thank the reviewers of the workshop for
reviewing our work and providing helpful feedback.

>>>>

\title{Old is Still Gold: A Comparison of Cyber and Traditional Consumer Fraud in The United States}

@@

While cybercrime is a relatively recent human invention, fraudulent activity
has a much longer history. Understanding the extent to which cybercrime is fundamentally different from, or similar to, traditional fraudulent activity is the first step toward being able to effectively combat it. This paper investigates the differences in fraud
reporting and targeting among United States based consumers by comparing
fraudulent activity mediated by the Internet with traditional forms of
fraud. By partitioning the FTC Consumer Sentinel complaint dataset into
cyber and traditional categories, we summarize the difference in fraud
trends across time, distance and location metrics. We also evaluate fraud
variations across different ethnic and socioeconomic factors. Our findings
suggest that reports of both categories of frauds decrease during
the holiday season. Individuals who are victimized via traditional methods
are more likely to complain using traditional methods, while a majority of
cyber victims submit fraud complaints online. By evaluating the top frauds
in each category, we demonstrate how traditional fraudsters have evolved in
their methodologies to execute scams on the Internet that were initially
perpetrated through traditional means.

@@

We would like to thank the reviewers for reviewing our work and providing
helpful feedback. This material is based upon work supported by the National Science Foundation
 under Grant No. 1351058. Any opinions,
findings, and conclusions or recommendations expressed in this material are
those of the authors and do not necessarily reflect the views of the
National Science Foundation.
